On the properties of discs around accreting brown dwarfs

### 2010-05-18 BD_disc/paper.tex
from laptop - th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2268 25464f21-6099-402c-b30a-640f1d40d38b

\title[**]{**}  \author[N.J.  Mayne and Tim
Harries]{N.J. Mayne$^{1}$\thanks{E-mail: nathan@astro.ex.ac.uk
    (NJM)} and Tim Harries$^{1}$\\
  $^{1}$ School of Physics,
  University of Exeter, Stocker Road, Exeter, EX4 4QL.\\
}
 \begin{document}

>>>>

\title[Brown dwarf discs]{On the properties of  discs around accreting brown dwarfs}  \author[Nathan J.  Mayne and Tim J. Harries]{Nathan J. Mayne\thanks{E-mail: nathan@astro.ex.ac.uk
    (NJM)} and Tim J. Harries\\
  School of Physics,
  University of Exeter, Stocker Road, Exeter, EX4 4QL.\\
}
 \begin{document}
